Offenses and Enforcement: A Study of Toronto’s Ticket Issuance Patterns

### 2024-09-24 paper/paper.qmd
First Draft

```{r}
#| label: tbl-meansdtickets
#| tbl-cap: Mean and standard deviation of Ticket Count
#| echo: false
#| warning: false
#| fig-align: center

@@

# Create summary table with formatted values
summary_table <- data.frame(
  Statistic = c("Total Tickets Issued", 
                "Mean Tickets Issued per Year", 
                "Standard Deviation of Yearly Tickets Issued"),
  Value = c(format(total_tickets, big.mark = ",", scientific = FALSE), 
            format(round(average_tickets_per_year$average, 2), big.mark = ",", scientific = FALSE), 
            format(round(std_dev_yearly_tickets$sd, 2), big.mark = ",", scientific = FALSE))
)

# Print the summary table using kable
kable(summary_table, format = "pipe", caption = "Summary Statistics for Ticket Issuance in Toronto from 2018-2023")

@@

```{r}
#| label: tbl-map
#| tbl-cap: Total Tickets Issued by Division
#| echo: false
#| warning: false
#| fig-align: center
# 1. Summarize ticket data by division 
tickets_summary <- cleaned_tickets_data %>% 
  group_by(Division) %>% 
  summarise(total_tickets = sum(`Ticket Count`, na.rm = TRUE))

>>>>

```{r}
#| label: tbl-meansdtickets
#| tbl-cap: Summary Statistics for Ticket Issuance in Toronto from 2018-2023
#| echo: false
#| warning: false
#| fig-align: center

@@

# Create summary table with formatted values
summary_table <- data.frame(
  `Summary Statistic` = c("Total Tickets Issued", 
                "Mean Tickets Issued per Year", 
                "Standard Deviation of Yearly Tickets Issued"),
  Value = c(format(total_tickets, big.mark = ",", scientific = FALSE), 
            format(round(average_tickets_per_year$average, 2), big.mark = ",", scientific = FALSE), 
            format(round(std_dev_yearly_tickets$sd, 2), big.mark = ",", scientific = FALSE))
)

# Print the summary table using kable
kable(summary_table, format = "pipe")

@@

```{r}
#| label: tbl-map
#| tbl-cap: Total Tickets Issued by Division
#| echo: false
#| warning: false
#| message: false
#| fig-align: center
# 1. Summarize ticket data by division 
tickets_summary <- cleaned_tickets_data %>% 
  group_by(Division) %>% 
  summarise(total_tickets = sum(`Ticket Count`, na.rm = TRUE))
